---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# associationr

<!-- badges: start -->
<!-- badges: end -->

The goal of associationr is to ...

## Installation

You can install the released version of associationr from [github](https://github.com/vitalinakomashko/associationr) with:

``` r
if (!("remotes" %in% installed.packages()[, "Package"])){
 install.packages("remotes")
}
remotes::install_github("vitalinakomashko/associationr")
```


## Parameters

As the first step you need to provide analysis parameters. Parameters should be
stored in a YAML file, see documentation about formatting [here](https://en.wikipedia.org/wiki/YAML).

Parameter | Meaning | Mandatory? | Values
----------|---------|-------------|-------
**primary_covs** | Main phenotype to be investigated |  YES | Column name in the sample annotation data frame
**adjust_covs** | Covariates to adjust for | YES | Column name in the sample annotation data frame
**test_method** | Method | YES | "limma" or "lm"
**interact_covs** |  If interactions should be investigated | NO | 
**block_covs** | If mixed-effect modeling should be performed | NO
**spline_fun** | If time-dependent effect should be investigated | NO | 
**ignore_sample_size** | | NO |
**voom** | If **voom** is provided then both **norm_factors_method** and **voom_normalize_method** must be provided | NO |  
**norm_factors_method** | Normalization method to be used for calculation of normalization factors to scale the raw library sizes| YES, if **voom** | "TMM", "TMMwsp", "RLE", "upperquartile", "none". See [edgeR::calcNormFactors](https://bioconductor.org/packages/release/bioc/html/edgeR.html) for documentation (v. 3.26.5).
**voom_normalize_method** | The microarray-style normalization method to be applied to the logCPM values (if any) | YES, if **voom** | "none", "scale", "quantile" or "cyclicloess". See [limma::voom](http://bioconductor.org/packages/release/bioc/html/limma.html) and [limma::normalizeBetweenArrays](http://bioconductor.org/packages/release/bioc/html/limma.html).

### Example of a YAML file with the analysis parameters

Quotes are not necessary around the values, both 'primary_covs: Group' and
'primary_covs: "Group"' are acceptable. 

```
primary_covs: Group
adjust_covs: Cov1
test_method: lm
interact_covs: Cov2
```
If the input data is RNA-seq and normalization factors should be calculated using
`edgeR::calcNormFactors` and the data should be transformed to prepare for linear
modeling using `limma::voom` then the following yaml formatting should be used: 

```
primary_covs: Group
adjust_covs: Cov1
test_method: lm
interact_covs: Cov2
voom:
 norm_factors_method: TMM
 voom_normalize_method: none
```



## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(associationr)
## basic example code
```

